%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume
\documentclass[margin,line]{resume}
\usepackage{hyperref}

%______________________________________________________________________________________________________________________
\begin{document}
\name {\Large Pralhad Jadhav}
\begin{resume}
    \hfill \textsl{Linkedin: \url{https://www.linkedin.com/in/pralhad-jadhav-7073b1174}} 
    %__________________________________________________________________________________________________________________

    \hfill \textsl{GitHub: \url{https://github.com/pralhad88}} 
    %__________________________________________________________________________________________________________________

     \hfill \textsl{Contact: +917666077878 pralhad@navgurukul.org} 
    %__________________________________________________________________________________________________________________
    
    % Skill
    \section{\mysidestyle Skill}
    Javascript, Python, Node.js, React.js, MySQL, AWS \vspace{-1.5mm}
    
    %__________________________________________________________________________________________________________________
    
    % Education
    \section {\mysidestyle Education}

    \textbf{B.Tech, ECE}, Sanjeevini College Of Engineering, Kopargaon \hfill \textbf{Aug 2012 -- May 2017}
    \begin{list2}
        \item Graduated with a 60 percent in a four year Electronics and Telecommunication Engineering course
    \end{list2}\vspace{-1.5mm}

    \textbf{Software Engineer}, NavGurukul, Dharmshala \hfill \textbf{May 2018 -- April 2019}
    \begin{list2}
        \item Attending a one-year residential course to learn Software Engineering and work on various projects​.
    \end{list2}\vspace{-1.5mm}

    %__________________________________________________________________________________________________________________
    
    % Professional Experience
    \section{\mysidestyle Professional\\Experience}
    \textbf{NavGurukul.org}, Software Engineer \hfill \textbf{April 2019 -- current}
    \begin{list2}
        \item Non-Profit to teach undeprivileged males and females to learn coding and get high paying jobs
        \item I have been working with Navgurukul for 1 year and 2 month and managing all technical and ​ complete admission pipelines for the admission team
        \item Giving some guidelines and teaching to Navgurukul students.
    \end{list2}\vspace{-1.5mm}

    \textbf{Freelancing}, Independence Freelancer \hfill \textbf{Dec 2019 -- current}
    \begin{list2}
        \item I started to do a freelancing from Dec 2019 and I work on one project but it is incompleted cause of COVID-19 the client is stoped their project.
    \end{list2}\vspace{-1.5mm}

    \textbf{Jiffy}, Technical Consultant \hfill \textbf{May 2020 -- June 2020}
    \begin{list2}
        \item The application is usable for business using Facebook page and user can create their own website using their facebook business page.
        \item I have been a technical consultant and leading project. The project is based on Node.js and react.js.
    \end{list2}\vspace{-1.5mm}

    %__________________________________________________________________________________________________________________
    
    % Projects
    \section{\mysidestyle Major\\Projects}
    \textbf{Gift a Deed}, React.js
    \\ Gift a deedi is a android base application to provide some emergency stuff for needy person I am cloning that into web application using react.js \url{https://github.com/pralhad88/React-GAD-app}.
    
    \textbf{NG Exceptions}, Python
    \\ I forked an existing library to create a tool for people to get python exceptions in Hindi. Using this module programmers can get different python exceptions translated into Hindi for better understanding.\url{https://github.com/pralhad88/ng_exception}.

    \textbf{Chat Bot}, Node.js
    \\ Here I implemented a basic version of a Daily Horoscop and Jokes API using express framework, cheerio and request module for scraping the data in Node.js.In this chat bot, if user wants to know his daily horoscope then it will give to us and if he is getting bored then ask to chat bot for some funny jokes it will give some jokes to them \url{https://github.com/pralhad88/Chat-bot_in_Node.js}.

    \textbf{Chanakya}, Node.js
    \\ Chanakya is an online testing platform used by the thousands of students who apply to get admission into Navgurukul. It helps manage and track the complete admission pipeline for the admission team. I took care of the end-to-end delivery of the complete platform \url{https://github.com/navgurukul/chanakya}.

    \textbf{Kalam}, React.js
    \\ Kalam is a user interface web application to interfacing all admission processes into Navgurukul. It helps to Navgurukul’s team for the entire admission process \url{https://github.com/navgurukul/kalam}

%______________________________________________________________________________________________________________________
\end{resume}
\end{document}


%______________________________________________________________________________________________________________________
% EOF